curatedMetagenomicData

### 2020-01-28 manuscript_NS_MRD.Rmd
updated

pseq.subset <- subset_samples(pseq.subset, !is.na(nationality) , !is.na(mnd) )
atlas.pseq <- subset_samples(atlas.pseq, !is.na(nationality), !is.na(mnd))

>>>>

pseq.subset <- subset_samples(pseq.subset, !is.na(nationality))
pseq.subset <- subset_samples(pseq.subset, !is.na(mnd))

#na.exclude(pseq.subset@sam_data[["mnd"]])

# Check mnd variable
# pseq.subset@sam_data[["mnd"]]

atlas.pseq <- subset_samples(atlas.pseq, !is.na(nationality), !is.na(mnd))
